Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-12-18 code/analysis.Rmd
updated cphiplot again

cplot <- c_over_phi %>%
  ggplot(aes(x = phi, y = C, color = factor(lab, levels = c("This study", "Fauria et al. (2015)")))) +
  geom_line(data = c_phi_curve, aes(x = phi, y = C), inherit.aes = FALSE) +
  geom_point(size = 2, pch = 4) +
  theme_bw() +
  labs(x = expression(paste("Collector Solid Volume Fraction (", phi[c], " )" )), color = "") +
  scale_color_manual(values = c("darkgreen","red")) +
  scale_x_continuous(labels = scales::percent)

>>>>

cplot <- c_over_phi %>%
  ggplot(aes(x = phi, y = C, pch = factor(lab, levels = c("This study", "Fauria et al. (2015)")), color = factor(lab, levels = c("This study", "Fauria et al. (2015)")))) +
  geom_line(data = c_phi_curve, aes(x = phi, y = C), inherit.aes = FALSE) +
  geom_point(size = 2) +
  theme_bw() +
  labs(x = expression(paste("Collector Solid Volume Fraction (", phi[c], " )" )), color = "", pch = "") +
  scale_color_manual(values = c("darkgreen","red")) +
  scale_x_continuous(labels = scales::percent)
